---
title: "Fall 2021 Data Science Intern Challenge"
author: "Candace Ng"
date: "April 28, 2021"
output: 
  html_document:
    theme: lumen
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, fig.width=8, fig.height=3)
```

### Question 1
The following analysis was done in R, where the data was read in through the provided spreadsheet saved as “shopify.csv”. Below is code to read in the dataset and to output column summaries. 
```{r}
dataset <- read.csv("shopify.csv")
summary(dataset)
```

a. The problem with the calculated value of $3145.13 is that this value is calculated across 100 different shops as opposed to each individual shop. We can filter the rows with order_amount greater than $1100 using the R command: 
```{r}
dataset[dataset$order_amount > 10000,c("order_id", "shop_id", "user_id", "order_amount", "total_items")]
```
Looking at the results, we notice that the shops with shop_id 42 and 78 are the only shops that have orders greater than $1100. Customers who order from the shop with shop_id 42 typically order in large quantities, while the shop with shop_id 78 sells sneakers for $25725 a pair. These two outliers significantly increase the average order value across the 100 different shops and thus this method of calculating the AOV is an unreliable measure to use. 

<br>
b. The metric I would use to report for this dataset is the average order value on a per shop_id basis. In R, we can aggregate the mean order amount by shop_id with the following R command:
```{r}
aggregate(dataset[,c("order_amount"),drop=FALSE], by=list(shop_id=dataset$shop_id), FUN=mean)
```

<br>
c. From the results of the command in part b above, we see that most shops have an average order value in the $200-$400 range. If we aggregate by total_items instead of order_amount, we see that most customers order 1-2 pairs of shoes per order.
```{r}
aggregate(dataset$total_items, by=list(shop_id=dataset$shop_id), FUN=mean)
```
These are reasonable numbers which would not have been obvious if the AOV was calculated over all 100 shops.

<hr>

### Question 2

<br>
a. 
```
select count(orderid) 
from orders o 
inner join shippers s on s.shipperid = o.shipperid
where s.shipperid = 1
```
Output: <b>54</b>

<br>
b. 
```
select top 1 productname
from ((products p
inner join orderdetails od on od.productid = p.productid)
inner join orders o on o.orderid = od.orderid)
inner join customers c on c.customerid = o.customerid
where country = 'Germany'
group by productname
order by count(productname) desc
```
Output: <b>Gorgonzola Telino</b>

<br>
c. 
```
select top 1 e.lastname
from (employees e 
inner join orders o on e.employeeid = o.employeeid)
group by e.lastname
order by count(orderid) desc
```
Output: <b>Peacock</b>